\begin{abstract}
  \thispagestyle{plain}
  \setcounter{page}{2}
  \addcontentsline{toc}{section}{Abstract}
Pressure ulcers are not only significantly affecting increased health costs, but are associated with increased mortality. In pressure ulcer stage I, skins are not broken but are discolored or red or may show changesin temperature or hardness compared to surrounding areas. And it at this stage can be reversed in about three days if all the pressures are taken off the site. However, it is also difficult to detect in individuals with dark skin tones.\\

This project is to explore the feasibility of using non-invasive techniques for the early detection of pressure ulcers. Emphasis will be placed on exploring a range of image processing and video analysis techniques and develop an practical non-invasive image-based pressure ulcer detection software.\\

For image processing, algorithms implemented are including brightness and contrast adjustment, histogram (RGB Histogram, Histogram Equalization, Contrast Limited Adaptive Equalizaiton) , filter (median filter, gaussian filter, Bilateral filter). Those methods have already proved available for detection of pressure ulcers in the previous research of Mohammed Umar Riyaz. and automatic pressure ulcers area detection. In the mean time, redness areas detection automatically is also developed. It is using contours as a curve joinging all the continuous points, having the same color(which is red in this case).\\

The videos were processed through eularian colour magnification. Eulerian Video Magnification is a  method capable of revealing temporal variations in videos that are impossible to see with the human naked eye. Using this method, it is possible to visualize the flow of blood as it fills the face, hands or legs.\\

Microsoft Visual C++ is the programming environment used to create this desktop applications. And use open resource OpenCV, which provides a common infrastructure for computer vision
applications and to accelerate the use of machine perception in the commercial products.
\end{abstract}