\appendix
\chapter{Software Engineering Methodology} \label{app:sem}
This project is more than producing a software but I consider it as a significant portion to be software engineering.  As such I will layout briefly how I plan to follow good practices. 

\begin{description}
\item[Version Control] I will keep my code (including all the reports) under version control using Git. Git is very useful to use on individual projects since it does not require setting up a server for repositories unlike centralized version control systems such as Subversion. Using Git also allows me to backup my code on Github where anyone can follow my progress if they want, \url{https://github.com/Shanshan-IC/MscProject}. 
For instance the source for this Latex document can be found at \url{https://github.com/Shanshan-IC/MscProject/Backgroundreport}.

\item[MATLAB] The software will be implemented image processing algorithms based on data test results on MATLAB image process toolbox.


\item[OpenCV] The software will be developed by Visual Studio 2012 with OpenCV. OpenCV (Open Source Computer Vision Library) is an open source computer vision and machine learning software library. OpenCV was built to provide a common infrastructure for computer vision applications and to accelerate the use of machine perception in the commercial products.

\item[Database] In the middle of stage, the software will be implemented the database to help nurses and doctors to store patients' skin analysis data and monitor the progress during the detection stage.

\item[Test Driven Developement] Test-driven development is an advanced technique that uses unit tests to drive the design of software. The suite of unit tests provides constant feedback that each component is still working and act as documentation that cannot go out-of-date.

\end{description}
