\chapter{Progress} 

I have already broken the project down into three main parts: modelling, implementation and evaluation. Modelling will focus on image process algorithms. In the implementation phase, the model is transformed in computer code and implemented into the software. During modelling and implementation are sufficiently far along that the code is producing results, then the evaluation stage can begin and results can be
analysed. Although separate they are not independent. For example, difficulties in implementation may require a rethink in the model, the implementation must include code that stores results for evaluation and evaluation of results may lead to changes in the model. Most of the progress so far has been on modelling and so I shall focus on it for this chapter.


\section{Progress summary} \label{prog:model}
A Medical Bsc student used linear normalisation, global histogram equalisation and contrast limited adaptive histogram equalisation to enhance image, and the videos were processed through eularian colour magnification. The findings in that report have confirmed that image processing can be used to improve image contrast and subsequently aid in the detection of erythema. This applies to all skin colours \cite{Mohammed}.
This report will using his findings and test more image process algorithms and implement them to the software.

\section{Plan}



\subsection{Implementation}
The process of implementing the image process methods into computer code must be broken down into smaller tasks. This will also include basic windows menu design, image adjustment methods, database setting, are appropriate to use. I have also given a brief description of the manner in which I plan to work in the Appendix \ref{app:sem}

\subsection{Evaluation}
In order to evaluate all the image process methods, it is necessary to decide
first what should be considered as successful outcomes and then how
these should be measured. For example, different images taken from nurses gains better effect results using different algorithm and why, and as a whole, which might be
measured as the best solution for analysis, setting it as default.
